---
output: 
    html_document:
        theme: flatly
title: "International tourism revenue in Brazil, by country"
author: "Ewerton Monti"
date: "25/07/2017"
---

```{r echo=FALSE, warning=FALSE, message=FALSE}
fileAddress <- "C:/Users/Ewerton/Dropbox/Curso_Data_Science/9_DataProducts/Week3/receita_turismo/receita_turismo.csv"
origData <- read.table(fileAddress, sep = ";", header = TRUE, 
                       colClasses = c("character", "numeric", "numeric", "numeric", "numeric", "character"))
```

This plot shows data about tourism expenditure in Brazil. The size of the circles represent the amount of revenue generated by tourists of each country in Brazil. Here, tourism revenue is the result of the multiplication of average daily expenditure per tourist in Brazil (y-axis of the plot), average length of stay in Brazil (x-axis of the plot) and number of tourists in Brazil - all data from 2016, for the most relevant countries.

Tourists from South America spent less money and made shorter stays in Brazil, compared to Europeans for example, but the amount of revenue they create is larger due to the number of tourists from those countries.

The plot was made using the plotly package.

The tablet below shows the first ten countries in tourism revenue in Brazil.

```{r warning=FALSE, message=FALSE}
library(plotly)
origData$revenue_format <- format(origData$revenue, decimal.mark = ",", big.mark = " ")
origData$tourists_format <- format(origData$tourists, decimal.mark = ",", big.mark = " ")
head(origData[order(-origData$revenue),1:6], n = 10)
```

Here is the plot and the code that creates it. 



```{r warning=FALSE} 
# Data for annotations
argentina <- origData[origData$country=="Argentina",]
usa <- origData[origData$country=="United States",]

# Plot
plot_ly(data = origData, 
        x = ~stay, 
        y = ~expenditure, 
        type = 'scatter',
        mode = 'markers',
        size = ~revenue,
        marker = list(sizeref = .05),
        color = ~region,
        colors = "Spectral",
        text = ~paste("Country: ", country, "<br>Tourists: ", tourists_format, '<br>Revenue: $', revenue_format, '<br>Average expenditure: $', expenditure, '<br>Average stay: ', stay, ' nights'),
        autosize = F, width = 900, height = 600
) %>%
    layout(
        title = 'Tourism in Brazil: total revenue, average expenditure and length of stay by country of origin',
        xaxis = list(title = "Average length of stay (nights)"),
        yaxis = list(title = "Average daily expenditure  per person (US$)")) %>%
    add_annotations(
        x = argentina$stay,
        y = argentina$expenditure,
        text = "Argentina creates<br>more revenue",
        xref = "x",
        yref = "y",
        showarrow = TRUE,
        arrowhead = 7,
        ax = -20,
        ay = -45) %>%
    add_annotations(
        x = usa$stay,
        y = usa$expenditure,
        text = "United States is the second in revenue creation",
        xref = "x",
        yref = "y",
        showarrow = TRUE,
        arrowhead = 7,
        ax = 20,
        ay = -45)
```


